\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.3 in,top=0.3in,right=0.3 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Everest K C} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1-208-957-4340 \\ \href{mailto:everestkc@everestkc.com.np}{everestkc@everestkc.com.np} \\ Redmond, WA} 
\address{ \href{https://everestkc.org}{everestkc.org} \\
\href{https://linkedin.com/in/babueverest}{linkedin.com/in/babueverest} \\
\href{https://github.com/everestkc}{github.com/everestkc} \\
\href{https://credly.com/users/everest-k-c/badges}{credly.com/users/everest-k-c}
} %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\vspace{-7pt}
\begin{rSection}{SUMMARY}
% {Software Engineer with 6+ years of experience in backend development, infrastructure automation, and site reliability engineering, seeking full-time Software Engineering roles. Skilled in designing backend services, automating CI/CD pipelines, and deploying cloud-native infrastructure using Python, Go, Bash, Linux, Docker, Kubernetes, Terraform, and Ansible.}
% {Software Engineer with 6+ years of experience building backend services, automations, CI/CD platforms, Linux-based systems, Kubernetes deployment workflows, and production observability. M.S. Computer Science graduate with a 4.0 GPA. Proven impact includes 90\% faster CI builds, 45\% faster offline upgrades, 30\% faster infrastructure deployment, and 25\% faster incident response through automation, testing, and monitoring.}
{Senior Software / Site Reliability Engineer with 6+ years building production-grade backend services, Linux-based systems, Kubernetes infrastructure, and CI/CD platforms. Delivered a 90\% CI build-time reduction, 75\% lower manual QA effort, 30\% faster infrastructure deployment, and 25\% faster incident response. Deep expertise in Python, Go, AWS, Kubernetes, distributed systems, and SLO-driven observability; equally effective as an SWE, SRE, or Production Engineer.}

% {Software Engineer and infrastructure-focused SRE with 6+ years of experience in backend development, infrastructure automation, and site reliability engineering, seeking full-time Software Engineering, DevOps, or SRE roles. Skilled in designing backend services, automating CI/CD pipelines, and deploying cloud-native infrastructure using Python, Go, Bash, Linux, Kubernetes, Docker, Terraform, and Ansible.}


\end{rSection}
%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Languages & Python, Go, C/C++, Java, Bash, SQL\\
% Technologies \& Tools & AWS (EC2, ECS, Lambda, S3, RDS, SQS, Boto3), Docker, Kubernetes, Terraform, Ansible,\\
% & Packer, Kafka, Apache Flink, gRPC, REST APIs, event-driven architecture, Prometheus,\\& Grafana, SLOs, Jenkins, GitHub Actions, PostgreSQL, MySQL, MongoDB,\\& Linux System Administration, ISO remastering

Languages & Python, Go, C/C++, Java, Bash, SQL\\
Cloud \& Infra & AWS, Azure, Docker, Kubernetes, Infrastructure as a Code, Terraform, Ansible, Packer\\
CI \& CD &  Git, Jenkins, GitHub Actions, Make, Gradle, ArgoCD, monorepo tooling (git-filter-repo)\\
Reliability \& Observability & Prometheus, Grafana, SLO/SLIs, alerting, incident response, postmortems\\
Distributed Systems \& Data & Kafka, Flink, gRPC, REST APIs, PostgreSQL, MySQL, MongoDB\\
Systems & Linux administration, ISO remastering, debootstrap, Debian Preseed, NixOS, Ubuntu

% Languages &  Python, Go, C/C++, Bash, Java, SQL\\
% Cloud & AWS (EC2, ECS, Lambda, S3, RDS, SQS, Boto3), Azure\\
% DevOps/Infra &  Make, Gradle, Docker, Kubernetes, Terraform, Ansible, Packer, Jenkins, GitHub Actions, GitLab CI\\
% Observability & Prometheus, Grafana\\
% Databases &  PostgreSQL, MySQL, MongoDB, Cassandra \\
% Technologies &  REST, gRPC, Kafka, Apache Flink, Airflow, Nginx, VMware ESXi\\
\end{tabular}
\end{rSection}

\begin{rSection}{EXPERIENCE}
\textbf{Graduate Assistant} \hfill Aug 2022 - May 2025\\
Boise State University \hfill \textit{Boise, ID}
% \textbf{Graduate Research Assistant}, Boise State University --- Boise, ID \hfill Aug 2022 -- May 2025
\vspace{-4pt}
\begin{itemize}
    \itemsep -3pt {}
    \item Researched privacy-preserving proximity search for geospatial systems using additive homomorphic encryption, order-preserving encryption, garbled-circuit-based secure comparison, and dummy-query obfuscation to evaluate and reduce hotspot inference risk; manuscript in preparation.
    \item Built reproducible \textbf{Python}/\textbf{SQL} experiment pipelines with \textbf{pandas}, \textbf{Bokeh}, and \textbf{Jenkins}, automating geospatial workload generation and hotspot inference evaluation, reducing turnaround \textbf{from days to hours} across repeated runs.
\end{itemize}

\textbf{Senior DevOps Engineer} \hfill Jul 2020 - Jul 2022\\
guardsix \hfill \textit{Lalitpur, Nepal}
\vspace{-4pt}
\begin{itemize}
    \itemsep -3pt {}
    \item Reduced CI build time by \textbf{90\%} from 50 min to 5 min by redesigning \textbf{Jenkins} pipelines, containerizing build environments, and authoring a \textbf{Go}-based parallel package download tool for reproducible release builds.
    \item Reduced PR cycle time by \textbf{35\%} via monorepo consolidation of \textbf{26 repos} using \textbf{git-filter-repo}, eliminating cross-repo dependency drift and simplifying code ownership.
    \item Provisioned AWS infra with \textbf{Terraform/Ansible/Packer} across 3 environments, cutting deployment time by \textbf{30\%}.
    \item Defined \textbf{SLOs, SLIs}, alerting thresholds, and on-call runbooks for \textbf{10 production services} using \textbf{Prometheus}/\textbf{Grafana}, reducing \textbf{MTTD} and \textbf{MTTR} by \textbf{25\%}.
    \item Led \textbf{blameless postmortems} and corrective-action tracking for recurring production incidents, eliminating recurrence of \textbf{3} major failure classes.
    \item Engineered monolith-to-microservices migration using the \textbf{Strangler Fig Pattern}, decomposing a legacy Python monolith into independently deployable \textbf{Kubernetes} services and reducing deployment frequency from weekly to daily.
    \item Reduced QA environment setup \textbf{from 2 hrs to 25 min} via \textbf{pyVmomi} automation, unblocking parallel QA lanes.
\end{itemize}

\textbf{Senior Software Engineer} \hfill Feb 2015 - Aug 2019\\
guardsix \hfill \textit{Lalitpur, Nepal}
\vspace{-4pt}
\begin{itemize}
    \itemsep -3pt {}
     \item Built \textbf{Python Flask} backend services using controlled subprocess execution to map Linux administration commands to a secure web-based management UI, standardizing server management.
    \item Built a \textbf{Django}/\textbf{SQL} customer portal for releases, documentation, and update notes, centralizing delivery for \textbf{500+ enterprise customers}.
    \item Led the design of a multi-tier (hot/warm/cold) \textbf{S3} and \textbf{Glacier} backup plugin for enterprise customers with \textbf{Boto3}.
    \item Built \textbf{Robot Framework} regression and upgrade-validation suites covering \textbf{150 test scenarios}, reducing manual QA cycle time by \textbf{75\%} and improving release confidence.
    \item Architected cumulative patch upgrade system for a custom \textbf{Linux OS} serving \textbf{2500+} air-gapped enterprise deployments and also reduced the upgrade time by \textbf{45\%}.
    \item Built custom \textbf{Ubuntu}-based Linux ISO through kernel compilation and ISO remastering with \textbf{debootstrap}, \textbf{Bash}, and \textbf{Debian Preseed}, integrating \textbf{ZFS, LVM}, monitoring agents, hardened defaults, and performance tuning.
    \item Built \textbf{Dockerized Kafka/Flink} edge-to-cloud pipelines ingesting \textbf{3000 events/sec} for a UEBA solution, enabling real-time behavioral anomaly detection at enterprise scale.
\end{itemize}
\end{rSection}

\begin{rSection}{Education}
{\bf Master of Science in Computer Science}, Boise State University \hfill {Aug 2022 - May 2026}\\
\hspace*{1em} \textit{\textbf{GPA:}} 4.0/4.0 \textbar{} \textit{\textbf{Research:}} \textit{Applied Cryptography, Privacy-Preserving Geospatial Systems}\\
{\bf Bachelor of Computer Engineering}, Tribhuvan University \hfill {Dec 2010 - Aug 2014}
\end{rSection}

\newpage

\begin{rSection}{Projects}
\textbf{AI-Powered Cloud Cost Advisor} \hfill Python, AWS, Bedrock, Cost Explorer, Lambda, S3
\begin{itemize}
    \item Built an AI assistant that analyzes AWS Cost Explorer data, identifies cost anomalies, and generates plain-English optimization recommendations for EC2, S3, Lambda, and idle resources.
    \item Used Amazon Bedrock to summarize cost trends and convert technical findings into business-friendly recommendations for engineering and finance stakeholders.
\end{itemize}

\textbf{RAG Assistant for Cloud Architecture Documentation} \hfill Python, Bedrock, LangChain, OpenSearch/Qdrant, S3
\begin{itemize}
    \item Built a retrieval-augmented generation assistant that answers architecture questions from internal runbooks, postmortems, Terraform modules, and AWS documentation.
    \item Implemented document ingestion, embeddings, vector search, and response grounding to help engineers quickly find operational and design guidance.
\end{itemize}

\textbf{Serverless AI Incident Triage Bot} \hfill AWS Lambda, CloudWatch, SNS, Bedrock, Python
\begin{itemize}
    \item Built a serverless incident triage workflow that consumes CloudWatch alarms, summarizes likely root causes, and recommends first-response actions using historical runbooks.
    \item Designed the workflow with event-driven architecture, least-privilege IAM permissions, and human-readable escalation summaries for on-call engineers.
\end{itemize}
\end{rSection}

\begin{rSection}{Certifications}
\textbf{Certified Information Systems Security Professional (CISSP)} \hfill Expires Oct 2028\\
\textbf{FinOps Certified Engineer} \hfill Expires Nov 2027\\
\textbf{Linux Foundation Certified System Administrator (LFCS)} \hfill Expires Jul 2026\\
\textbf{Certified Kubernetes Administrator (CKA)} \hfill Expires Aug 2026\\
\textbf{AWS Certified Solutions Architect -- Associate} \hfill Expired Dec 2024
\end{rSection}



%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Curricular Activities} 
% \begin{itemize}
%     \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
%     \item	Sample bullet point.
% \end{itemize}


% \end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Projects} 
% \textbf{InfraSage RAG} \hfill Python, OpenAI API, Chroma, Streamlit
% \begin{itemize}
%     \item Built a RAG-based technical knowledge assistant that ingests runbooks, PDFs, and infrastructure documents to answer questions using retrieved context.
% \end{itemize}

% \textbf{RepoPilot Agent} \hfill Python, OpenAI API, Tool Calling, GitHub API
% \begin{itemize}
%     \item Developed an AI agent that analyzes GitHub repositories, identifies project dependencies, and generates setup, build, and debugging instructions.
% \end{itemize}

% \textbf{PyPackageOracle} \hfill Python, Streamlit, SerpApi, GPT-4o
% \begin{itemize}
%     \item Built an AI-powered Python package recommendation engine that searches developer sources and ranks libraries with pros, cons, alternatives, and evidence-backed verdicts.
% \end{itemize}
% % \begin{itemize}
% %     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% % \end{itemize}


% \end{rSection}


\end{document}
